Astronomical Image colorization and up-scaling with generative adversarial networks\\

### 2021-09-27 Research Paper/IEEE/paper.tex
Added ICLR

We train models using both color spaces and compare their performance.
\subsection{Mathematical Model}
\subsubsection{Generative Adversarial Networks}
 A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.
\begin{figure*}[!htb]
    \centering
    \input{figures/tex_files/gan_visualization.tex}
    \caption{Approach for image colorization using conditional GANs}
    \label{fig:gan_visualization}
\end{figure*}
  Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
  $$G(x) = \hat{y}$$

>>>>

We train models using both color spaces and compare their performance.
\subsection{Mathematical Model}
\subsubsection{Generative Adversarial Networks}
 A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.
\begin{figure*}[!htb]
    \centering
    \input{figures/tex_files/gan_visualization.tex}
    \caption{Approach for image colorization using conditional GANs. A sample grayscale image is provided as an input to the generator and the generated image along with the ground truth is fed to the discriminator. The probability \textit{p} is the probability that the discriminator thinks the two images are similar.}
    \label{fig:gan_visualization}
\end{figure*}
  Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
  $$G(x) = \hat{y}$$
